Demo arXiv template

### 2022-10-31 paper/paper.qmd
section 2 draft

The concept of pipeline (and pipe) is not a new concept to computing. It refers to a set of data processing elements connected in series, where the output of one element is the input of the next one.
@wickham_plumbing_2009 argues that whether made explicit or not, pipeline has to be presented in every graphics program.
The paper also argues that breaking down graphic rendering into steps is beneficial for understand the implementation and compare between different graphic systems. 
The discussion on pipeline construction is well documented in early interactive graphics software: @buja_elements_1988, @sutherland_orca_2000, and @xie_reactive_2014 and their pipeline steps include non-linear transformation, variable standardization, randomization and dimension reduction.

@@

One of the most commonly known pipeline example is perhaps the Unix pipeline where programs can be concatenated with `|` to flow the output from the last program into the next program. 
The pipeline design avoid writing a complicated program to solve a complex problem but building simple programs that do one thing well and work well together.
This design philosophy is also embraced in the R community by the tidyverse principles. 
In tidyverse, the flow from the previous program to the next is ensured through reusing the tidy data format [@wickham_tidy_2014], which prescribes three rules on how to layout tabular data.
To solve a complicated data problem using tidyverse, one typically builds the solution using a collection of functions and these functions have a strong human centered design with intuitive naming and easy to reference through autocomplete.

**A proper pipeline example in R: tidymodel**

A pipeline example in R that adopts the tidyverse principle is the tidymodel suite [@tidymodels] for building machine learning models. 
The machine learning pipeline constitutes data resampling, feature engineering, model fitting, model tuning, and model evaluation each being responsible by a separate package. 
Before tidymodel, analysts who wish to fit different models need to learn the workflow of each individual algorithm and need to rewrite most of the model fitting, tuning, and evaluation code when switching from one model to another. 
The tidymodel approach unifies a wide range of models under a single pipeline where users can substitute different models while maintain the same pipeline.
This allows users to easily experiment with different machine learning models a lot easier.

@@

*more work here*

Both arguments are applicable to index construction.
Papers that proposing new indices always present a workflow diagram to illustrate how data is transformed into the final indices, but not much implementation has explicitly present this this step-by-step transformation in the code design.
Constructing indices also involves this working pattern of trials and errors on different options before finding the final solution. A tidy workflow will give researchers more flexibility to tune the steps as they wish and while maintain a readable and intuitive code base.

>>>>

Data pipeline is not a new concept to computing. It refers to a set of data processing elements connected in series, where the output of one element is the input of the next one.
@wickham_plumbing_2009 argues that whether made explicit or not, the pipeline has to be presented in every graphics program.
The paper also argues that breaking down graphic rendering into steps is beneficial for understanding the implementation and comparing between different graphic systems. 
The discussion on pipeline construction is well documented in early interactive graphics software: @buja_elements_1988, @sutherland_orca_2000, and @xie_reactive_2014 and their pipeline steps include non-linear transformation, variable standardization, randomization and dimension reduction.

@@

One of the most commonly known pipeline examples is perhaps the Unix pipeline where programs can be concatenated with `|` to flow the output from the last program into the next program, i.e.

````
command 1 | command 2 | command 3 | ...
````

To solve a complex problem, the Unix system builds simple programs that do one thing well and work well together.
This design is also reflected in the tidyverse ecosystem in R.
To solve a complicated data problem using tidyverse, analysts typically build the solution using a collection of tools from the tidyverse toolbox. 
The data object can flow smoothly from one command to the next, safeguarded by the tidy data format [@wickham_tidy_2014], which prescribes three rules on how to lay out tabular data.
The tidyverse tools also embrace a strong human-centered design where function names are intuitive and easy to reference through autocomplete.
With the tidyverse design principle in mind, the tidymodel suite enables analysts to build machine learning models through the data pipeline. 
It includes typical tasks required in machine learning like data resampling, feature engineering, model fitting, model tuning, and model evaluation.
An advantage of tidymodel pipeline over separate software for individual models is that analysts no longer need to write model-specific syntax to work with each model, but pipeline-specific syntax that is applicable to all the models implemented in tidymodel.
This allows users to easily experiment with a collection of machine learning models.

@@

In index construction, data pipeline is often presented in a workflow diagram in the research paper to illustrate how the raw data is transformed into the final indices. 
This agrees with Wickham's argument on the presence of the data pipeline, however, more often than not, the pipeline is not made explicit in the software.
Often the time, all the steps are lumped into a single wrapper function, rather than being split into smaller, modulated functions. 
This increases the cost of maintaining and understanding the code base, gives analysts little freedom to customise the indices for specific needs, and hinders reusing existing code for building new indices.
A pipeline approach unites a range of indices under a single data pipeline and analysts can compose indices from pipeline steps like building Legos from individual bricks.
In this workflow, analysts are not limited by indices that have been already proposed and can easily combine pipeline steps to compose novel indices.  Analysis of the indices (i.e. calculation of uncertainty) is also feasible by adding external code into the pipeline.

### 2022-10-31 paper/paper.tex
section 2 draft

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, interior hidden, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

The concept of pipeline (and pipe) is not a new concept to computing. It
refers to a set of data processing elements connected in series, where
the output of one element is the input of the next one. Wickham et al.
(2009) argues that whether made explicit or not, pipeline has to be
presented in every graphics program. The paper also argues that breaking
down graphic rendering into steps is beneficial for understand the
implementation and compare between different graphic systems. The
discussion on pipeline construction is well documented in early
interactive graphics software: Buja et al. (1988), Sutherland et al.
(2000), and Xie, Hofmann, and Cheng (2014) and their pipeline steps
include non-linear transformation, variable standardization,
randomization and dimension reduction.

@@

One of the most commonly known pipeline example is perhaps the Unix
pipeline where programs can be concatenated with \texttt{\textbar{}} to
flow the output from the last program into the next program. The
pipeline design avoid writing a complicated program to solve a complex
problem but building simple programs that do one thing well and work
well together. This design philosophy is also embraced in the R
community by the tidyverse principles. In tidyverse, the flow from the
previous program to the next is ensured through reusing the tidy data
format (Wickham 2014), which prescribes three rules on how to layout
tabular data. To solve a complicated data problem using tidyverse, one
typically builds the solution using a collection of functions and these
functions have a strong human centered design with intuitive naming and
easy to reference through autocomplete.

\textbf{A proper pipeline example in R: tidymodel}

A pipeline example in R that adopts the tidyverse principle is the
tidymodel suite (Kuhn and Wickham 2020) for building machine learning
models. The machine learning pipeline constitutes data resampling,
feature engineering, model fitting, model tuning, and model evaluation
each being responsible by a separate package. Before tidymodel, analysts
who wish to fit different models need to learn the workflow of each
individual algorithm and need to rewrite most of the model fitting,
tuning, and evaluation code when switching from one model to another.
The tidymodel approach unifies a wide range of models under a single
pipeline where users can substitute different models while maintain the
same pipeline. This allows users to easily experiment with different
machine learning models a lot easier.

@@

\emph{more work here}

Both arguments are applicable to index construction. Papers that
proposing new indices always present a workflow diagram to illustrate
how data is transformed into the final indices, but not much
implementation has explicitly present this this step-by-step
transformation in the code design. Constructing indices also involves
this working pattern of trials and errors on different options before
finding the final solution. A tidy workflow will give researchers more
flexibility to tune the steps as they wish and while maintain a readable
and intuitive code base.

@@

\leavevmode\vadjust pre{\hypertarget{ref-tidymodels}{}}%
Kuhn, Max, and Hadley Wickham. 2020. \emph{Tidymodels: A Collection of
Packages for Modeling and Machine Learning Using Tidyverse Principles.}
\url{https://www.tidymodels.org}.

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, frame hidden, boxrule=0pt, sharp corners, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

Data pipeline is not a new concept to computing. It refers to a set of
data processing elements connected in series, where the output of one
element is the input of the next one. Wickham et al. (2009) argues that
whether made explicit or not, the pipeline has to be presented in every
graphics program. The paper also argues that breaking down graphic
rendering into steps is beneficial for understanding the implementation
and comparing between different graphic systems. The discussion on
pipeline construction is well documented in early interactive graphics
software: Buja et al. (1988), Sutherland et al. (2000), and Xie,
Hofmann, and Cheng (2014) and their pipeline steps include non-linear
transformation, variable standardization, randomization and dimension
reduction.

@@

One of the most commonly known pipeline examples is perhaps the Unix
pipeline where programs can be concatenated with \texttt{\textbar{}} to
flow the output from the last program into the next program, i.e.~

\begin{verbatim}
command 1 | command 2 | command 3 | ...
\end{verbatim}

To solve a complex problem, the Unix system builds simple programs that
do one thing well and work well together. This design is also reflected
in the tidyverse ecosystem in R. To solve a complicated data problem
using tidyverse, analysts typically build the solution using a
collection of tools from the tidyverse toolbox. The data object can flow
smoothly from one command to the next, safeguarded by the tidy data
format (Wickham 2014), which prescribes three rules on how to lay out
tabular data. The tidyverse tools also embrace a strong human-centered
design where function names are intuitive and easy to reference through
autocomplete. With the tidyverse design principle in mind, the tidymodel
suite enables analysts to build machine learning models through the data
pipeline. It includes typical tasks required in machine learning like
data resampling, feature engineering, model fitting, model tuning, and
model evaluation. An advantage of tidymodel pipeline over separate
software for individual models is that analysts no longer need to write
model-specific syntax to work with each model, but pipeline-specific
syntax that is applicable to all the models implemented in tidymodel.
This allows users to easily experiment with a collection of machine
learning models.

@@

In index construction, data pipeline is often presented in a workflow
diagram in the research paper to illustrate how the raw data is
transformed into the final indices. This agrees with Wickham's argument
on the presence of the data pipeline, however, more often than not, the
pipeline is not made explicit in the software. Often the time, all the
steps are lumped into a single wrapper function, rather than being split
into smaller, modulated functions. This increases the cost of
maintaining and understanding the code base, gives analysts little
freedom to customise the indices for specific needs, and hinders reusing
existing code for building new indices. A pipeline approach unites a
range of indices under a single data pipeline and analysts can compose
indices from pipeline steps like building Legos from individual bricks.
In this workflow, analysts are not limited by indices that have been
already proposed and can easily combine pipeline steps to compose novel
indices. Analysis of the indices (i.e.~calculation of uncertainty) is
also feasible by adding external code into the pipeline.

@@
